Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
address a result todo

\todo{One sentence introducing this experiment.}
To determine if core team member's have greater build success rates,
we classified the build success rate for
core team members and non-core team members in the data set without 
downsampling.  We found that core team members
triggered 89.39\% of the builds in the data set and 75.58\% of those builds
passed.  Non-core team members triggered 10.61\% of the builds in the data set
and 64.70\% of the builds passed.  This shows that core team members are more
likely to have a successful build integration than non-core team members.

>>>>

Based on the decision tree results, we noticed that core team members where
important when classifying build success, so we decided to investigate if core
team members have greater build success rates.
We classified the build success rate for
core team members and non-core team members using the data set without 
downsampling.  We found that core team members
triggered 89.39\% of the builds in the data set and 75.58\% of those builds
passed.  Non-core team members triggered 10.61\% of the builds in the data set
and 64.70\% of the builds passed.  This shows that core team members are more
likely to have a successful build integration than non-core team members.
